Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-01-30 Paper.tex
\hypertarget{R l}{}Thus

\usepackage{tabu} %requires array.

%This should be the last package before \input{Version.tex}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
% "hyperref loads the url package internally. Use \PassOptionsToPackage{hyphens}{url}\usepackage{hyperref} to pass the option to the url package when it is loaded by hyperref. This avoids any package option clashes." Source: <https://tex.stackexchange.com/questions/3033/forcing-linebreaks-in-url/3034#comment44478_3034>. 
% Note also this: "If the \PassOptionsToPackage{hyphens}{url} approach does not work, maybe it's "because you're trying to load the url package with a specific option, but it's being loaded by one of your packages before that with a different set of options. Try loading the url package earlier than the package that requires it. If it's loaded by the document class, try using \RequirePackage[hyphens]{url} before the document class." Source: <https://tex.stackexchange.com/questions/3033/forcing-linebreaks-in-url/3034#comment555944_3034>.
% For more information on using the hyperref package, refer to e.g. https://en.wikibooks.org/w/index.php?title=LaTeX/Hyperlinks&stable=0#Hyperlink_and_Hypertarget.

\makeatletter
 \newcommand{\linkdest}[1]{\Hy@raisedlink{\hypertarget{#1}{}}}
\makeatother
\usepackage{seqsplit}

% For formatting
%\usepackage{underscore}
%\usepackage{lipsum} % to generate filler text for testing of document rendering
\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\MakeOuterQuote{"}

@@

The transaction receipt is a tuple of four items comprising the cumulative gas used in the block containing the transaction receipt as of immediately after the transaction has happened, $R_u$, the set of logs created through execution of the transaction, $R_\mathbf{l}$ and the Bloom filter composed from information in those logs, $R_b$ and the status code of the transaction, $R_z$:
\begin{equation}
R \equiv (R_z, R_u, R_b, R_\mathbf{l})
\end{equation}

@@

We assert that the status code $R_z$ is an integer.
\begin{equation}
R_z \in \mathbb{P}
\end{equation}

@@

\hypertarget{block_header_without_nonce_and_mixmash_h__cancel_n}{}Where $H_{\hcancel{n}}$ is the new block's header $H$, but \textit{without} the nonce and mix-hash components, $\mathbf{d}$ being the current DAG, a large data set needed to compute the mix-hash, and $\mathtt{PoW}$ is the proof-of-work function (see section \ref{ch:pow}): this evaluates to an array with the first item being the mix-hash, to proof that a correct DAG has been used, and the second item being a pseudo-random number cryptographically dependent on $H$ and $\mathbf{d}$. Given an approximately uniform distribution in the range $[0, 2^{64})$, the expected time to find a solution is proportional to the difficulty, $H_d$.

@@

\hypertarget{block_header_validity_function}{}Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv &  n \leqslant \frac{2^{256}}{H_d} \wedge m = H_m \quad \wedge \\
& & H_d = D(H) \quad \wedge \\
& & H_g \le H_l  \quad \wedge \\
& & H_l < {P(H)_H}_l + \left\lfloor\frac{{P(H)_H}_l}{1024}\right\rfloor  \quad \wedge \\
& & H_l > {P(H)_H}_l - \left\lfloor\frac{{P(H)_H}_l}{1024}\right\rfloor  \quad \wedge \\
& & H_l \geqslant 5000  \quad \wedge \\
& & H_s > {P(H)_H}_s \quad \wedge \\
& & H_i = {P(H)_H}_i +1 \quad \wedge \\
& & \lVert H_x \rVert \le 32
\end{eqnarray}
where $(n, m) = \mathtt{PoW}(H_{\hcancel{n}}, H_n, \mathbf{d})$

@@

Thus $\boldsymbol{\sigma}'$ is the post-transactional state. We also define $\Upsilon^g$ to evaluate to the amount of gas used in the execution of a transaction, $\Upsilon^\mathbf{l}$ to evaluate to the transaction's accrued log items and $\Upsilon^z$ to evaluate to the status code resulting from the transaction. These will be formally defined later.

@@

\hypertarget{self_destruct_set_wordy_defn}{}The tuple contents include $A_\mathbf{s}$, the self-destruct set: a set of accounts that will be discarded following the transaction's completion.\hypertarget{tx_log_series_wordy_defn}{} $A_\mathbf{l}$ is the log series: this is a series of archived and indexable `checkpoints' in VM code execution that allow for contract-calls to be easily tracked by onlookers external to the Ethereum world (such as decentralised application front-ends).\hypertarget{tx_touched_accounts_wordy_defn}{} $A_\mathbf{t}$ is the set of touched accounts, of which the empty ones are deleted at the end of a transaction.\hypertarget{refund_balance_defn_words}{} Finally there is $A_r$, the refund balance, increased through using the {\small SSTORE} instruction in order to reset contract storage to zero from some non-zero value. Though not immediately refunded, it is allowed to partially offset the total execution costs.

@@

\subsection{Execution}
\hypertarget{intrinsic_gas_g_0}{}We define intrinsic gas $g_0$, the amount of gas this transaction requires to be paid prior to execution, as follows:
\begin{align}
g_0 \equiv {} & \sum_{i \in T_\mathbf{i}, T_\mathbf{d}} \begin{cases} G_{txdatazero} & \text{if} \quad i = 0 \\ G_{txdatanonzero} & \text{otherwise} \end{cases} \\
{} & + \begin{cases} G_\text{txcreate} & \text{if} \quad T_t = \varnothing \\ 0 & \text{otherwise} \end{cases} \\
{} & + G_{transaction}
\end{align}

@@

The validity is determined as:
\begin{equation}
\begin{array}[t]{rcl}
S(T) & \neq & \varnothing \quad \wedge \\
\boldsymbol{\sigma}[S(T)] & \neq & \varnothing \quad \wedge \\
\linkdest{transaction_nonce}{}T_n & = & \boldsymbol{\sigma}[S(T)]_n \quad \wedge \\
g_0 & \leqslant & T_g \quad \wedge \\
v_0 & \leqslant & \boldsymbol{\sigma}[S(T)]_b \quad \wedge \\
T_g & \leqslant & {B_H}_l - \ell(B_\mathbf{R})_u
\end{array}
\end{equation}

@@

The final state, $\boldsymbol{\sigma}'$, is reached after deleting all accounts that either appear in the self-destruct list or are touched and empty:
\begin{eqnarray}
\boldsymbol{\sigma}' & \equiv & \boldsymbol{\sigma}^* \quad \text{except} \\
\linkdest{self_destruct_list_A__s}{}\forall i \in A_\mathbf{s}: \boldsymbol{\sigma}'[i] & = & \varnothing \\
\linkdest{touched_A__t}{}\forall i \in A_\mathbf{t}: \boldsymbol{\sigma}'[i] & = & \varnothing \quad\text{if}\quad \mathtt{\tiny DEAD}(\boldsymbol{\sigma}^*\kern -2pt, i)
\end{eqnarray}

\hypertarget{tx_total_gas_used_Upsilon_pow_g}{}\hypertarget{tx_logs_Upsilon_pow_l}{}\hypertarget{tx_status_Upsilon_pow_s}{}And finally, we specify $\Upsilon^g$, the total gas used in this transaction, $\Upsilon^\mathbf{l}$, the logs created by this transaction and $\Upsilon^z$, the status code of this transaction:
\begin{eqnarray}
\Upsilon^g(\boldsymbol{\sigma}, T) & \equiv & T_g - g' \\
\Upsilon^\mathbf{l}(\boldsymbol{\sigma}, T) & \equiv & A_\mathbf{l} \\
\Upsilon^z(\boldsymbol{\sigma}, T) & \equiv & z
\end{eqnarray}

@@

\begin{equation}
(\boldsymbol{\sigma}^{**}, g^{**}, A, \mathbf{o}) \equiv \Xi(\boldsymbol{\sigma}^*, g, I, \{s, a\}) \\
\end{equation}
\pagebreak[1]where $I$ contains the parameters of the execution environment as defined in section \ref{ch:model}, that is:\pagebreak[1]
\begin{eqnarray}
I_a & \equiv & a \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & () \\
I_s & \equiv & s \\
I_v & \equiv & v \\
I_\mathbf{b} & \equiv & \mathbf{i} \\
I_e & \equiv & e \\
I_w & \equiv & w
\end{eqnarray}

@@

\begin{itemize}
\item\linkdest{address_of_account_which_owns_code_I__a_def_words}{} $I_a$, the address of the account which owns the code that is executing.
\item\linkdest{address_of_sender_of_tx_that_originated_execution_I__o}{} $I_o$, the sender address of the transaction that originated this execution.
\item\linkdest{gas_price_in_tx_that_originated_execution_I__p}{} $I_p$, the price of gas in the transaction that originated this execution.
\item\linkdest{execution_input_data_I__d}{} $I_\mathbf{d}$, the byte array that is the input data to this execution; if the execution agent is a transaction, this would be the transaction data.
\item\linkdest{the_address_of_the_account_which_caused_the_code_to_be_executing_I__s}{} $I_s$, the address of the account which caused the code to be executing; if the execution agent is a transaction, this would be the transaction sender.
\item\linkdest{Wei_value_exec}{} $I_v$, the value, in Wei, passed to this account as part of the same procedure as execution; if the execution agent is a transaction, this would be the transaction value.
\item\linkdest{exec_machine_code_I__b}{} $I_\mathbf{b}$, the byte array that is the machine code to be executed.
\item\linkdest{exec_block_header_I__H}{} $I_H$, the block header of the present block.
\item\linkdest{exec_call_or_create_depth_I__e}{} $I_e$, the depth of the present message-call or contract-creation (i.e. the number of {\small CALL}s or {\small CREATE}s being executed at present).
\item\linkdest{exec_permission_to_modify_state_I__w}{} $I_w$, the permission to make modifications to the state.
\end{itemize}

@@

As previously detailed, $\mathbf{R}[n]_z$, $\mathbf{R}[n]_\mathbf{l}$ and $\mathbf{R}[n]_u$ are the $n$th corresponding status code, logs and cumulative gas used after each transaction ($\mathbf{R}[n]_b$, the fourth component in the tuple, has already been defined in terms of the logs). We also define the $n$th state $\boldsymbol{\sigma}[n]$, which is defined simply as the state resulting from applying the corresponding transaction to the state resulting from the previous transaction (or the block's initial state in the case of the first such transaction):
\begin{equation}
\boldsymbol{\sigma}[n] = \begin{cases} \Gamma(B) & \text{if} \quad n < 0 \\ \Upsilon(\boldsymbol{\sigma}[n - 1], B_\mathbf{T}[n]) & \text{otherwise} \end{cases}
\end{equation}

@@

We define $\mathbf{R}[n]_z$ in a similar manner.
\begin{equation}
\mathbf{R}[n]_z =
\Upsilon^z(\boldsymbol{\sigma}[n - 1], B_\mathbf{T}[n])
\end{equation}

@@

Thus we finish by formally defining $R_l$:
\begin{eqnarray}
R_l(\mathbf{x}) & \equiv & \begin{cases}
(192 + \lVert s(\mathbf{x}) \rVert) \cdot s(\mathbf{x}) & \text{if} \quad \lVert s(\mathbf{x}) \rVert < 56 \\
\big(247 + \big\lVert \mathtt{\tiny BE}(\lVert s(\mathbf{x}) \rVert) \big\rVert \big) \cdot \mathtt{\tiny BE}(\lVert s(\mathbf{x}) \rVert) \cdot s(\mathbf{x}) & \text{otherwise}
\end{cases} \\
s(\mathbf{x}) & \equiv & \mathtt{\tiny RLP}(\mathbf{x}_0) \cdot \mathtt{\tiny RLP}(\mathbf{x}_1) ...
\end{eqnarray}

@@

We assert the functions $\mathtt{\small ECDSASIGN}$, $\mathtt{\small ECDSARECOVER}$ and $\mathtt{\small ECDSAPUBKEY}$. These are formally defined in the literature.
\begin{eqnarray}
\mathtt{\small ECDSAPUBKEY}(p_r \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64} \\
\linkdest{ECDSASIGN}{}\mathtt{\small ECDSASIGN}(e \in \mathbb{B}_{32}, p_r \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{\small ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64}
\end{eqnarray}

Where $p_u$ is the public key, assumed to be a byte array of size 64 (formed from the concatenation of two positive integers each $< 2^{256}$) and $p_r$ is the private key, a byte array of size 32 (or a single positive integer in the \hypertarget{v}{}aforementioned range). It is assumed that $v$ is either the `recovery identifier' or `chain identifier doubled plus 35 or 36'. The recovery identifier is a 1 byte value specifying the parity and finiteness of the coordinates of the curve point for which $r$ is the x-value; this value is in the range of $[27, 30]$, however we declare the upper two possibilities, representing infinite values, invalid. The value 27 represents an even $y$ value and 28 represents an odd $y$ value.

@@

\begin{tabular*}{\columnwidth}[h]{lrl}
\toprule
Name & Value & Description \\
\midrule
\linkdest{Jwordbytes}{}$J_{wordbytes}$ & 4  & Bytes in word. \\
$J_{datasetinit}$ & $2^{30}$ & Bytes in dataset at genesis. \\
$J_{datasetgrowth}$ & $2^{23}$ & Dataset growth per epoch. \\
$J_{cacheinit}$ & $2^{24}$ & Bytes in cache at genesis. \\
$J_{cachegrowth}$ & $2^{17}$ & Cache growth per epoch. \\
$J_{epoch}$ & 30000 & Blocks per epoch. \\
$J_{mixbytes}$ & 128 & mix length in bytes. \\
$J_{hashbytes}$ & 64 & Hash length in bytes. \\
$J_{parents}$ & 256 & Number of parents of each dataset element. \\
$J_{cacherounds}$ & 3 & Number of rounds in cache production. \\
$J_{accesses}$ & 64 & Number of accesses in hashimoto loop. \\
\bottomrule
\end{tabular*}

@@

\subsection{Deletion of an Account Despite Out-of-gas}

At block 2675119, in the transaction \seqsplit{0xcf416c536ec1a19ed1fb89e\\4ec7ffb3cf73aa413b3aa9b77d60e4fd81a4296ba}, an account at address 0x03 was called and an out-of-gas occurred during the call. Against the equation (\ref{eq:pre}), this added 0x03 in the set of touched addresses, and this transaction turned $\boldsymbol{\sigma}[0x03]$ into $\varnothing$.

\section{List of mathematical symbols}\label{app:symbols}
\begin{tabu*}{X[l]X[c]X} \savetabu{col3}
\toprule
Symbol & Latex Command & Description \hypertarget{bigvee}{}\\
\midrule
$\bigvee$ & \verb|\bigvee| & This is the least upper bound, supremum, or join of all elements operated on. Thus it is the greatest element of such elements \cite{Davey2002_zbMATH01748069}.\\
\bottomrule
\end{tabu*}

>>>>

% I will insert other table packages in here after this is merged.

%This should be the last package before \input{Version.tex}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
% "hyperref loads the url package internally. Use \PassOptionsToPackage{hyphens}{url}\usepackage{hyperref} to pass the option to the url package when it is loaded by hyperref. This avoids any package option clashes." Source: <https://tex.stackexchange.com/questions/3033/forcing-linebreaks-in-url/3034#comment44478_3034>. 
% Note also this: "If the \PassOptionsToPackage{hyphens}{url} approach does not work, maybe it's "because you're trying to load the url package with a specific option, but it's being loaded by one of your packages before that with a different set of options. Try loading the url package earlier than the package that requires it. If it's loaded by the document class, try using \RequirePackage[hyphens]{url} before the document class." Source: <https://tex.stackexchange.com/questions/3033/forcing-linebreaks-in-url/3034#comment555944_3034>.

@@

The transaction receipt is a tuple of four items comprising the cumulative gas used in the block containing the transaction receipt as of immediately after the transaction has happened, $R_u$, the set of logs created through execution of the transaction, $R_\mathbf{l}$ and the Bloom filter composed from information in those logs, $R_b$ and the status code of the transaction, $R_{s'}$:
\begin{equation}
R \equiv (R_u, R_b, R_\mathbf{l}, R_{s'})
\end{equation}

@@

We assert that the status code $R_{s'}$ is an integer.
\begin{equation}
R_{s'} \in \mathbb{P}
\end{equation}

@@

Where $H_{\hcancel{n}}$ is the new block's header $H$, but \textit{without} the nonce and mix-hash components, $\mathbf{d}$ being the current DAG, a large data set needed to compute the mix-hash, and $\mathtt{PoW}$ is the proof-of-work function (see section \ref{ch:pow}): this evaluates to an array with the first item being the mix-hash, to proof that a correct DAG has been used, and the second item being a pseudo-random number cryptographically dependent on $H$ and $\mathbf{d}$. Given an approximately uniform distribution in the range $[0, 2^{64})$, the expected time to find a solution is proportional to the difficulty, $H_d$.

@@

Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv &  n \leqslant \frac{2^{256}}{H_d} \wedge m = H_m \quad \wedge \\
& & H_d = D(H) \quad \wedge \\
& & H_g \le H_l  \quad \wedge \\
& & H_l < {P(H)_H}_l + \left\lfloor\frac{{P(H)_H}_l}{1024}\right\rfloor  \quad \wedge \\
& & H_l > {P(H)_H}_l - \left\lfloor\frac{{P(H)_H}_l}{1024}\right\rfloor  \quad \wedge \\
& & H_l \geqslant 5000  \quad \wedge \\
& & H_s > {P(H)_H}_s \quad \wedge \\
& & H_i = {P(H)_H}_i +1 \quad \wedge \\
& & \lVert H_x \rVert \le 32
\end{eqnarray}
where $(n, m) = \mathtt{PoW}(H_{\hcancel{n}}, H_n, \mathbf{d})$

@@

Thus $\boldsymbol{\sigma}'$ is the post-transactional state. We also define $\Upsilon^g$ to evaluate to the amount of gas used in the execution of a transaction and $\Upsilon^\mathbf{l}$ to evaluate to the transaction's accrued log items, both to be formally defined later.

@@

The tuple contents include $A_\mathbf{s}$, the self-destruct set: a set of accounts that will be discarded following the transaction's completion. $A_\mathbf{l}$ is the log series: this is a series of archived and indexable `checkpoints' in VM code execution that allow for contract-calls to be easily tracked by onlookers external to the Ethereum world (such as decentralised application front-ends). $A_\mathbf{t}$ is the set of touched accounts, of which the empty ones are deleted at the end of a transaction. Finally there is $A_r$, the refund balance, increased through using the {\small SSTORE} instruction in order to reset contract storage to zero from some non-zero value. Though not immediately refunded, it is allowed to partially offset the total execution costs.

@@

\subsection{Execution}
We define intrinsic gas $g_0$, the amount of gas this transaction requires to be paid prior to execution, as follows:
\begin{align}
g_0 \equiv {} & \sum_{i \in T_\mathbf{i}, T_\mathbf{d}} \begin{cases} G_{txdatazero} & \text{if} \quad i = 0 \\ G_{txdatanonzero} & \text{otherwise} \end{cases} \\
{} & + \begin{cases} G_\text{txcreate} & \text{if} \quad T_t = \varnothing \\ 0 & \text{otherwise} \end{cases} \\
{} & + G_{transaction}
\end{align}

@@

The validity is determined as:
\begin{equation}
\begin{array}[t]{rcl}
S(T) & \neq & \varnothing \quad \wedge \\
\boldsymbol{\sigma}[S(T)] & \neq & \varnothing \quad \wedge \\
T_n & = & \boldsymbol{\sigma}[S(T)]_n \quad \wedge \\
g_0 & \leqslant & T_g \quad \wedge \\
v_0 & \leqslant & \boldsymbol{\sigma}[S(T)]_b \quad \wedge \\
T_g & \leqslant & {B_H}_l - \ell(B_\mathbf{R})_u
\end{array}
\end{equation}

@@

The final state, $\boldsymbol{\sigma}'$, is reached after deleting all accounts that either appear in the self-destruct list or are touched and empty:
\begin{eqnarray}
\boldsymbol{\sigma}' & \equiv & \boldsymbol{\sigma}^* \quad \text{except} \\
\forall i \in A_\mathbf{s}: \boldsymbol{\sigma}'[i] & = & \varnothing \\
\forall i \in A_\mathbf{t}: \boldsymbol{\sigma}'[i] & = & \varnothing \quad\text{if}\quad \mathtt{\tiny DEAD}(\boldsymbol{\sigma}^*\kern -2pt, i)
\end{eqnarray}

And finally, we specify $\Upsilon^g$, the total gas used in this transaction, $\Upsilon^\mathbf{l}$, the logs created by this transaction and $\Upsilon^{s}$, the status code of this transaction:
\begin{eqnarray}
\Upsilon^g(\boldsymbol{\sigma}, T) & \equiv & T_g - g' \\
\Upsilon^\mathbf{l}(\boldsymbol{\sigma}, T) & \equiv & A_\mathbf{l} \\
\Upsilon^s(\boldsymbol{\sigma}, T) & \equiv & s'
\end{eqnarray}

@@

\begin{equation}
(\boldsymbol{\sigma}^{**}, g^{**}, A, \mathbf{o}) \equiv \Xi(\boldsymbol{\sigma}^*, g, I, \{s, a\}) \\
\end{equation}
where $I$ contains the parameters of the execution environment as defined in section \ref{ch:model}, that is:
\begin{eqnarray}
I_a & \equiv & a \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & () \\
I_s & \equiv & s \\
I_v & \equiv & v \\
I_\mathbf{b} & \equiv & \mathbf{i} \\
I_e & \equiv & e \\
I_w & \equiv & w
\end{eqnarray}

@@

\begin{itemize}
\item $I_a$, the address of the account which owns the code that is executing.
\item $I_o$, the sender address of the transaction that originated this execution.
\item $I_p$, the price of gas in the transaction that originated this execution.
\item $I_\mathbf{d}$, the byte array that is the input data to this execution; if the execution agent is a transaction, this would be the transaction data.
\item $I_s$, the address of the account which caused the code to be executing; if the execution agent is a transaction, this would be the transaction sender.
\item $I_v$, the value, in Wei, passed to this account as part of the same procedure as execution; if the execution agent is a transaction, this would be the transaction value.
\item $I_\mathbf{b}$, the byte array that is the machine code to be executed.
\item $I_H$, the block header of the present block.
\item $I_e$, the depth of the present message-call or contract-creation (i.e. the number of {\small CALL}s or {\small CREATE}s being executed at present).
\item $I_w$, the permission to make modifications to the state.
\end{itemize}

@@

As previously detailed, $\mathbf{R}[n]_{s'}$, $\mathbf{R}[n]_\mathbf{l}$ and $\mathbf{R}[n]_u$ are the $n$th corresponding status code, logs and cumulative gas used after each transaction ($\mathbf{R}[n]_b$, the fourth component in the tuple, has already been defined in terms of the logs). We also define the $n$th state $\boldsymbol{\sigma}[n]$, which is defined simply as the state resulting from applying the corresponding transaction to the state resulting from the previous transaction (or the block's initial state in the case of the first such transaction):
\begin{equation}
\boldsymbol{\sigma}[n] = \begin{cases} \Gamma(B) & \text{if} \quad n < 0 \\ \Upsilon(\boldsymbol{\sigma}[n - 1], B_\mathbf{T}[n]) & \text{otherwise} \end{cases}
\end{equation}

@@

We define $\mathbf{R}[n]_{s'}$ in a similar manner.
\begin{equation}
\mathbf{R}[n]_{s'} =
\Upsilon^{s}(\boldsymbol{\sigma}[n - 1], B_\mathbf{T}[n])
\end{equation}

@@

\hypertarget{R l}{}Thus we finish by formally defining $R_l$:
\begin{eqnarray}
R_l(\mathbf{x}) & \equiv & \begin{cases}
(192 + \lVert s(\mathbf{x}) \rVert) \cdot s(\mathbf{x}) & \text{if} \quad \lVert s(\mathbf{x}) \rVert < 56 \\
\big(247 + \big\lVert \mathtt{\tiny BE}(\lVert s(\mathbf{x}) \rVert) \big\rVert \big) \cdot \mathtt{\tiny BE}(\lVert s(\mathbf{x}) \rVert) \cdot s(\mathbf{x}) & \text{otherwise}
\end{cases} \\
s(\mathbf{x}) & \equiv & \mathtt{\tiny RLP}(\mathbf{x}_0) \cdot \mathtt{\tiny RLP}(\mathbf{x}_1) ...
\end{eqnarray}

@@

We assert the functions $\mathtt{\small ECDSASIGN}$, $\mathtt{\small ECDSARECOVER}$ and $\mathtt{\small ECDSAPUBKEY}$. These are formally defined in the literature.
\begin{eqnarray}
\mathtt{\small ECDSAPUBKEY}(p_r \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64} \\
\mathtt{\small ECDSASIGN}(e \in \mathbb{B}_{32}, p_r \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{\small ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64}
\end{eqnarray}

Where $p_u$ is the public key, assumed to be a byte array of size 64 (formed from the concatenation of two positive integers each $< 2^{256}$) and $p_r$ is the private key, a byte array of size 32 (or a single positive integer in the aforementioned range). It is assumed that $v$ is either the `recovery identifier' or `chain identifier doubled plus 35 or 36'. The recovery identifier is a 1 byte value specifying the parity and finiteness of the coordinates of the curve point for which $r$ is the x-value; this value is in the range of $[27, 30]$, however we declare the upper two possibilities, representing infinite values, invalid. The value 27 represents an even $y$ value and 28 represents an odd $y$ value.

@@

\begin{tabular*}{\columnwidth}[h]{lrl}
\toprule
Name & Value & Description \\
\midrule
$J_{wordbytes}$ & 4  & Bytes in word. \\
$J_{datasetinit}$ & $2^{30}$ & Bytes in dataset at genesis. \\
$J_{datasetgrowth}$ & $2^{23}$ & Dataset growth per epoch. \\
$J_{cacheinit}$ & $2^{24}$ & Bytes in cache at genesis. \\
$J_{cachegrowth}$ & $2^{17}$ & Cache growth per epoch. \\
$J_{epoch}$ & 30000 & Blocks per epoch. \\
$J_{mixbytes}$ & 128 & mix length in bytes. \\
$J_{hashbytes}$ & 64 & Hash length in bytes. \\
$J_{parents}$ & 256 & Number of parents of each dataset element. \\
$J_{cacherounds}$ & 3 & Number of rounds in cache production. \\
$J_{accesses}$ & 64 & Number of accesses in hashimoto loop. \\
\bottomrule
\end{tabular*}

@@

\subsection{Deletion of an Account Dispite Out-of-gas}

At block 2675119, in the transaction \texttt{0xcf416c536ec1a19ed1fb89e4ec7ffb3cf73aa413b3aa9b77d60e4fd81a4296ba}, an account at address 0x03 was called and an out-of-gas occurred during the call. Against the equation (\ref{eq:pre}), this added 0x03 in the set of touched addresses, and this transaction turned $\boldsymbol{\sigma}[0x03]$ into $\varnothing$.
